Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2016-10-02 paper.tex
Do not hyphenate 'overpredict'

There are many examples in the literature of 2-D cross-flow turbine simulations
with widely varying results. Balduzzi et al.~\cite{Balduzzi2016} provides a
summary of recent efforts and an attempt to standardize a methodology for using
Reynolds-averaged Navier--Stokes (RANS) to correctly predict performance of a
2-D CFT. Howell et al.~\cite{Howell2010}, performed both 2-D and 3-D simulations
of a high solidity cross-flow turbine using a $k$--$\epsilon$ renormalization
group (RNG) turbulence model. The results from the 2-D simulations
over-predicted power coefficient since the rotor had a low aspect ratio, while
the 3-D case matched well with wind tunnel measurements near the tip speed ratio
of maximum power. In general, 3-D simulations are less common, but have begun to
appear more frequently recently---a testament to the progress towards higher
computing power.

@@

A cross-flow turbine was modeled using the $k$--$\omega$ SST and
Spalart--Allmaras (SA) Reynolds-averaged Navier--Stokes turbulence models to
test their abilities to predict turbine performance and near-wake dynamics. It
was observed that when modeled in 2-D, performance is over-predicted compared to
the data from the tow tank experiments, which was expected due to omission of
blade end effects, support strut drag, and increased blockage. Vertical (or
axial) wake dynamics were unresolved in the 2-D model, despite being identified
as a significant contributor to streamwise wake recovery, which casts doubt on
the 2-D model's applicability as a tool to study array spacing effects.

>>>>

There are many examples in the literature of 2-D cross-flow turbine simulations
with widely varying results. Balduzzi et al.~\cite{Balduzzi2016} provides a
summary of recent efforts and an attempt to standardize a methodology for using
Reynolds-averaged Navier--Stokes (RANS) to correctly predict performance of a
2-D CFT. Howell et al.~\cite{Howell2010}, performed both 2-D and 3-D simulations
of a high solidity cross-flow turbine using a $k$--$\epsilon$ renormalization
group (RNG) turbulence model. The results from the 2-D simulations
overpredicted power coefficient since the rotor had a low aspect ratio, while
the 3-D case matched well with wind tunnel measurements near the tip speed ratio
of maximum power. In general, 3-D simulations are less common, but have begun to
appear more frequently recently---a testament to the progress towards higher
computing power.

@@

A cross-flow turbine was modeled using the $k$--$\omega$ SST and
Spalart--Allmaras (SA) Reynolds-averaged Navier--Stokes turbulence models to
test their abilities to predict turbine performance and near-wake dynamics. It
was observed that when modeled in 2-D, performance is overpredicted compared to
the data from the tow tank experiments, which was expected due to omission of
blade end effects, support strut drag, and increased blockage. Vertical (or
axial) wake dynamics were unresolved in the 2-D model, despite being identified
as a significant contributor to streamwise wake recovery, which casts doubt on
the 2-D model's applicability as a tool to study array spacing effects.
